Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-01 Arxiv/main.tex
rearrange
update contents table

 % \documentclass[sigconf]{acmart}
\documentclass{article}

% We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}
\usepackage{accents}

@@

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \cite{dimitrakakis2014robust}, and
\cite{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

@@

\begin{equation*}
\begin{split}
Pr[u(\hexpmech(\dataobs)) \leq c] 
& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
\end{split}
\end{equation*}

which has been used in the dilation property proof.

@@

\subsection{Computation Efficiency Optimization}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$ 
can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
by applying the distance triangle property.

@@

\subsection{Theoretical Results}

@@

\subsection{Experimental Results}
\label{subsec_vs_variables}

@@

\subsection{Experiment Evaluations on Privacy Loss}
\label{subsec_experiment_privacy}
In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section. The $(\epsilon, \delta)$ - differential privacy we proved in Sec. \ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism. We calculate the concrete privacy value in following ways wrt. the data size, and obtain plots in Fig. \ref{fig_privacy}.

>>>>

 % \documentclass[sigconf]{acmart}
\documentclass{article}
% We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}

@@

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\footnotesize \tableofcontents}

\newpage
\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \cite{dimitrakakis2014robust}, and
\cite{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

@@

\begin{equation*}
\begin{split}
Pr[u(\hexpmech(\dataobs)) \leq c] 
& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}),
\end{split}
\end{equation*}
which has been used in the dilation property proof.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$ 
can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
by applying the distance triangle property.

@@

\subsection{Accuracy Evaluation}
\subsubsection{Theoretical Results}

@@

\subsubsection{Experimental Results}
\label{subsec_vs_variables}

@@

\subsection{Privacy Evaluation}
\label{subsec_experiment_privacy}
In order to see our privacy behavior, we study the accurate epsilon under concrete cases in this section. The $(\epsilon, \delta)$ - differential privacy we proved in Sec. \ref{subsec_hexpmech} is just an upper bound, we concrete $\epsilon$ should be smaller than upper bound in our exponential mechanism. We calculate the concrete privacy value in following ways wrt. the data size, and obtain plots in Fig. \ref{fig_privacy}.
